Individual and Differential Harm in Redistricting

### 2022-12-06 paper/harm.Rmd
readability
typo

In general, $q$ harms some individuals while $\tilde q$, and $\tilde q$ harms a distinct, though not necessarily disjoint, set of individuals.
A symmetric version of $h_i(v,q,\tilde q)$ would need to combine both of these groups: those harmed and those who gain by electing their chosen candidate under $q$ but not under the counterfactual $\tilde q$.
In practice, voters, courts, or politicians may differ in their views on how to balance preventing harm and maximizing gains.

@@

```{r alabama-harm-sample, fig.width=6.5}
#| fig.cap: |
#|      On thel eft, the expected fraction of voters in each precinct which are
#|      harmed by the 2020 enacted congressional districts versus the sampled 
#|      counterfactual set.
#|      On the right, the expected number of harmed voters in each race/partisan 
#|      group, relative to the total number of such voters.
include_graphics("figures/al_harm_sample.pdf")
```

>>>>

In general, $q$ harms some individuals versus $\tilde q$, and $\tilde q$ harms a distinct, though not necessarily disjoint, set of individuals, versus $q$.
A symmetric version of $h_i(v,q,\tilde q)$ would need to combine both of these groups: those harmed and those who gain by electing their chosen candidate under $q$ but not under the counterfactual $\tilde q$.
In practice, voters, courts, or politicians may differ in their views on how to balance preventing harm and maximizing gains.

@@

```{r alabama-harm-sample, fig.width=6.5}
#| fig.cap: |
#|      On the left, the expected fraction of voters in each precinct which are
#|      harmed by the 2020 enacted congressional districts versus the sampled 
#|      counterfactual set.
#|      On the right, the expected number of harmed voters in each race/partisan 
#|      group, relative to the total number of such voters.
include_graphics("figures/al_harm_sample.pdf")
```
